\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
% \usepackage{helvetica}
% \usepackage{array}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{0.1375in}
%\addtolength{\textheight}{1.75in}
\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% \textit{#3} &  \\
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\[-0.2cm]

\resheading{\textbf{\large Positions of Responsibility} }\\[\lsep] \\[-0.3cm]
\begin{itemize}
  

	\item \textbf{Teaching Assistant for CS101} (Computer Programming) \emph{Jan'17-May'17}\\[-0.6cm]
	\begin{itemize}
    \item Mentored  undergrad students in weekly labs and resolved students’ doubts in lab sessions\\[-0.5cm]
    \item Evaluated exams and lab assignments\\[-0.5cm]
	\end{itemize}
\item \textbf{Teaching Assistant for CS347m} (Operating System Mionor) \emph{July'17-Till Date}\\[-0.6cm]
	\begin{itemize}
		\item Presented a demo on "Basic command  of linux"  and prepared code snippet for "Basics of Scripting".\\[-0.5cm]
	    \item Coordinated assessment and grading of quizzes, exam answer sheets,Project	
	\end{itemize}

\item \textbf{Teaching Assistant for CS475M} (Computer Graphics Minor) \emph{Jul'16-Nov'16}\\[-0.6cm]
\end{itemize}
\vskip 0.15in

\resheading{\textbf{\large Achievements and Extra Curricular Activities}}\\[\lsep]\\[-0.3cm]
\begin{itemize}
  \item Secured \textbf{1st} rank in State Level Essay Writing competition organized by Rajsthan Patrika
  	\item Participated in Technical Events in\textbf{ National Level Techno-Management Colloquium  NU Tech'15 } at Nirma University,Ahmedabad.
  	\item Participated in Mini Marathon \textbf{The Republic Run}  held at Ahmedabad.
  \item Completed \textbf{Trekking Expedition} organized by INVINCIBLE NGO at Kalatop in Jan 2015.
  \item \textbf{Hobbies:} Volleyball, Trekking, listening music
\end{itemize}

\resheading{\textbf{\large Project And Seminar} }\\[\lsep]\\[-0.3cm]
\begin{itemize}
\item \textbf { Attribute Based Access Control}: Studied various research papers which focused on lattice-based model like ABAC,RBAC,RWFM.Classified and compared the various lattice-based model. 

	\end{itemize}

\begin{itemize}
\item \textbf{ Sketched Baesd Character Animation}: Studied various research papers which focused on how to generate 3D model from 2D sketch. Surveyed  the various  techniques studied  so that we can use that in character animation.
	\end{itemize}

\begin{itemize}
\item \textbf{Road Condition Management System}:A Web-based application which shows features of the road and provide map and database solution.
 It is established for for collecting data of the road network. 
\end{itemize}

\begin{itemize}
\item \textbf{Image Fusion In Medical Images}:Studied basic  fusion algorithms for images and their applications.
\end{itemize}
\begin{itemize}
\item published a paper \textbf{Comparative Study of Image Fusion Techniques for Medical Applications} in journal \textbfComputer Science and Communication (ISSN 0973-7391)}
\emph{(co-author: \textbf{Prof.Rupal Kapdi },  May'15)}\\[-0.6cm]
\end{itemize}


\resheading{\textbf{\large Other projects} }\\[\lsep]\\[-0.3cm]

\begin{itemize}

\item {Online Bookstore }
 \hfill\emph{Software Lab} \\[-0.6cm]
	

\item {Toonify
} 
  \hfill\emph{Foundation of Digital Image Processing } \\[-0.6cm]


\item {Carrom player
} 
  \hfill\emph{Foundation Of Intelligent And Learning Agents } \\[-0.6cm]
	

	
\end{itemize}

\resheading{\textbf{\large Technical Exposure} }\\[\lsep]\\[-0.3cm]

 \begin{itemize}
  \item \textbf{Languages}: C, C++,Python, Shell Scripting, awk, sed,Assembly \\[-0.55cm] 
  \item \textbf{Web Technologies }: HTML, PHP, CSS, JavaScript,MySql \\[-0.55cm] 
 \item \textbf{Tools and IDE}: Wireshark, \LaTeX, Git, Gnuplot ,Phonegap,Matlab,VC++\\[-0.6cm]
  \end{itemize}


\end{document}
