\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
% \usepackage{helvetica}
% \usepackage{array}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{0.1375in}
%\addtolength{\textheight}{1.75in}
\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% \textit{#3} &  \\
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\[-0.2cm]

\resheading{\textbf{\large M.Tech. Project} }\\[\lsep]
\begin{itemize}
\item \textbf { Attribute Based Access Control}\\
 \emph{(Advisor: \textbf{Prof. R.K.Shyamasundar}, June'17 - Till Date)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Studied various research papers which focused on lattice-based model like ABAC,RBAC.
	\item  Classified and compared the various lattice-based model. 
	\item Reviewed research papers which focused on RWFM problem.
	\item Currently studying how can we approach purpose-based privacy policies using RWFM

	\end{itemize}

\end{itemize}



\resheading{\textbf{\large M.Tech. Seminar} }\\[\lsep]
\begin{itemize}
\item \textbf{ Sketched Baesd Character Animation
} \\
 \emph{(Advisor: \textbf{Prof. Parag Chaudhuri}, Jan’17-May’17)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Studied various research papers which focused on how to generate 3D model from 2D sketch.
 	\item Surveyed  the various  techniques studied  so that we can use that in character animation.

	\end{itemize}
\end{itemize}





\resheading{\textbf{\large Course Projects}}\\[\lsep]

\begin{itemize}
\item \textbf{Toonify: Cartoon Photo Effect Application} \\
\emph{	CS663 (Advisor: \textbf{Prof. Suyash Awate}, July'16-Nov'16)}\\[-0.6cm]
      \begin{itemize}\itemsep \isep
	    \item Studied an research paper and analyzed  {\bf Toonify: Cartoon Photo Effect Application} .
		\item Implemented algorithm given in the paper which gives cartoon effect to photos.
      \end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{carrom  Player} \\
\emph{CS747 (Advisor: \textbf{Prof. Shivram }, July'16-Nov'16)}\\[-0.6cm]
      \begin{itemize}\itemsep \isep
	    \item  implemented an agent to play the game of Carrom
	    \item The agent can play in both 1-player mode (to clear the board using a minimal number of strikes) and in 2-player mode.


      \end{itemize}
\end{itemize}
\begin{itemize}
\item \textbf{Online BookStore} \\
\emph{CS699 (Advisor: \textbf{Prof. Bhaskaran Raman}, Jan'16-May'16)}\\[-0.6cm]
      \begin{itemize}\itemsep \isep
	    \item  Implemented web application using HTML,PHP and MySQL, designed frontend User Interface and backend database
		\itemAllowed student to login,search book, upload book, view list of books and download books	
      \end{itemize}
\end{itemize}


\clearpage

\resheading{\textbf{\large Undergraduate Project} }\\[\lsep]\\[-0.3cm]
\begin{itemize}
\item \textbf{Road Condition Management System}\\
 \emph{(Advisor: \textbf{Prof.Kruti Lavingia}, Jan'1-May'16)} \\[-0.6cm]
      \begin{itemize}\itemsep \isep
	    \item A Web-based application which shows features of the road and provide map and database solution.
		 \item It is established for for collecting data of the road network. 
		 \item Front end was built in HTML,CSS,Javascript  and back end was built in Mysql ,php.
\end{itemize}
\end{itemize}

\resheading{\textbf{\large Undergraduate Seminar} }\\[\lsep]\\[-0.3cm]
\begin{itemize}
\item \textbf{Image Fusion In Medical Images}\\
 \emph{(Advisor: \textbf{Prof. Rupal Kapadi}, Jan'15-May'15)} \\[-0.6cm]
      \begin{itemize}\itemsep \isep
	    \item Studied basic  fusion algorithms for images and their applications.
		 \item compared and classified image fusion techniques.
		 \item published a paper on \textbf {Comparative Study of Image Fusion Techniques for Medical Applications}
\end{itemize}
\end{itemize}

\resheading{\textbf{\large Technical Exposure}}\\[\lsep]\\[-0.3cm]
 \begin{itemize}
  \item \textbf{Languages}: C, C++,Python, Shell Scripting, awk, sed,Assembly \\[-0.55cm] 
  \item \textbf{Web Technologies }: HTML, PHP, CSS, JavaScript,MySql \\[-0.55cm] 
 \item \textbf{Tools and IDE}: Wireshark, \LaTeX, Git, Gnuplot \\[-0.6cm]
  \item \textbf{Area Of Interest}: Image Processing
  \end{itemize}

\resheading{\textbf{\large Publication} }\\[\lsep]
\begin{itemize}
\item \textbf{Comparative Study of Image Fusion Techniques for Medical Applications} \\
\emph{(co-author: \textbf{Prof.Rupal Kapdi },  May'15)}\\[-0.6cm]
      \begin{itemize}\itemsep \isep 
	    \item Published a paper  {\bf Comparative Study of Image Fusion Techniques for Medical Applications}in journal \textbfComputer Science and Communication (ISSN 0973-7391)}
	    \item It presents categories of basic fusion algorithms for
medical images.
\item It also present comparative study of variety of pixel based methods along with its advantages and disadvantages is covered.

\end{itemize}
\end{itemize}


\resheading{\textbf{\large Positions of Responsibility} }\\[\lsep]
\begin{itemize}
  

	\item \textbf{Teaching Assistant for CS101} (Computer Programming) \emph{Jan'17-May'17}\\[-0.6cm]
	\begin{itemize}
    \item Mentored  undergrad students in weekly labs and resolved students’ doubts in lab sessions\\[-0.5cm]
    \item Evaluated exams and lab assignments\\[-0.5cm]
	\end{itemize}
\item \textbf{Teaching Assistant for CS347m} (Operating System Mionor) \emph{July'17-Till Date}\\[-0.6cm]
	\begin{itemize}
		\item Presented a demo on "Basic command  of linux"  and prepared code snippet for "Basics of Shell Scripting".\\[-0.5cm]
	    \item Coordinated assessment and grading of quizzes, exam answer sheets,Project	
	\end{itemize}

\item \textbf{Teaching Assistant for CS475M} (Computer Graphics Minor) \emph{Jul'16-Nov'16}\\[-0.6cm]
\end{itemize}
\vskip 0.15in


\resheading{\textbf{\large Achievements and Extra Curricular Activities}}\\[\lsep]\\[-0.3cm]
\begin{itemize}
  \item Secured \textbf{1st} rank in State Level Essay Writing competition organized by Rajsthan Patrika
  	\item Participated in Technical Events in\textbf{ National Level Techno-Management Colloquium  NU Tech'15 } at Nirma University
  	\item Participated in Mini Marathon \textbf{The Republic Run}  held at Ahmedabad.
  \item Completed \textbf{Trekking Expedition} organized by INVINCIBLE NGO at Kalatop in Jan 2015.
  \item \textbf{Hobbies:} Volleyball, Trekking, listening music
\end{itemize}





\resheading{\textbf{\large Graduation Courses }}\\[\lsep]\\[0.3cm]
	\noindent\begin{minipage}{.60\textwidth}
		\begin{itemize}
			\item Operating Systems\\[-0.6cm]
			\item Object Oriented Programming\\[-0.6cm]
			\item computer Graphics\\[-0.5cm]
			
			
		\end{itemize}
	\end{minipage} 
	\noindent\begin{minipage}{.40\textwidth}
		\begin{itemize}
			\item Data Structure And Algorithms\\[-0.6cm]
			\item Computer Networks\\[-0.6cm]
			\item Database Management System\\[-0.5cm]
					
		\end{itemize}
	\end{minipage}



\end{document}
